GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-10-15 ennv.tex
update

>>>>

\section{Types of Neural Networks}

\paragraph{Convolutional Neural Networks} Convolutional Neural Networks (CNNs) are a type of neural network that is often used in image recognition and classification. CNNs are designed to automatically and adaptively learn spatial hierarchies of features from input images. CNNs are made up of neurons that have learnable weights and biases. Each neuron receives several inputs, takes a weighted sum over them, passes it through an activation function, and responds with an output.

\paragraph{Recurrent Neural Networks} Recurrent Neural Networks (RNNs) are a type of neural network that is often used in natural language processing and speech recognition. RNNs are designed to recognize patterns in sequences of data. RNNs have loops in them, allowing information to persist. This loop allows information to be passed from one step of the network to the next.

\paragraph{Generative Adversarial Networks} Generative Adversarial Networks (GANs) are a type of neural network that is often used in generating new data. GANs are made up of two networks, a generator and a discriminator. The generator creates new data instances, while the discriminator evaluates them for authenticity. The goal of the generator is to generate data that is indistinguishable from real data, while the goal of the discriminator is to correctly classify real and generated data.

\paragraph{Autoencoders} Autoencoders are a type of neural network that is often used in unsupervised learning. Autoencoders are designed to learn efficient representations of data. Autoencoders consist of an encoder and a decoder. The encoder compresses the input data into a lower-dimensional representation, while the decoder reconstructs the input data from the lower-dimensional representation.

\paragraph{Residual Networks} Residual Networks (ResNets) are a type of neural network that is often used in image recognition and classification. ResNets are designed to address the vanishing gradient problem that occurs in deep neural networks. ResNets introduce skip connections that allow the gradient to flow directly through the network, making it easier to train deep networks.
